Modularly Composing Typed Language Fragments (Supplemental Material)

### 2014-11-06 att-pldi15/att-pldi15-supplement.tex
Near final main paper

\inferrule[args-s]{
    \keyw{args}(\es)=_{n} \st
}{
    \keyw{args}(\es;e)=_{n+1} \skap{\karg}{\svar{rcons}}~\st~(\slam{\kty}{\svar{ty}}{\sana{n}{\svar{ty}}},\slam{\kunit}{\_}{\ssyn{n}})
}
\end{mathpar}
We assume that the definitions of the standard helper functions $\small\svar{nil} :: \kforall{\kalpha}{\klist{\kalpha}}$ and $\small\svar{rcons} :: \kforall{\kalpha}{\klist{\kalpha} \rightarrow \kalpha \rightarrow \klist{\kalpha}}$, which adds an item to the end of a list, have been substituted into these rules. The result is that the $n$th element of the argument interface list simply wraps the static terms $\sana{n}{\st}$ and $\ssyn{n}$.

>>>>

\inferrule[args-s]{
    \keyw{args}(\es)=_{n} \st
}{
    \keyw{args}(\es;e)=_{n+1} \skap{\karg}{\svar{rcons}}~\st~(\slam{\kty}{\svar{ty}}{\sana{n}{\svar{ty}}},\slam{\kunit}{\_}{\ssyn{n}})
}
\end{mathpar}

\begin{mathpar}\small
\inferrule[s-itm-anatrans-v]{
    \sval{\st}{\es;\Upsilon;\Phi}\\
    \keyw{nth}[n](\es)=e
}{
    \sval{\sqitm{\anatrans{n}{\st}}}{\es;\Upsilon;\Phi}
}

\inferrule[s-itm-syntrans-v]{
    \keyw{nth}[n](\es)=e
}{
    \sval{\sqitm{\syntrans{n}}}{\es;\Upsilon;\Phi}
}
\end{mathpar}

We assume that the definitions of the standard helper functions $\small\svar{nil} :: \kforall{\kalpha}{\klist{\kalpha}}$ and $\small\svar{rcons} :: \kforall{\kalpha}{\klist{\kalpha} \rightarrow \kalpha \rightarrow \klist{\kalpha}}$, which adds an item to the end of a list, have been substituted into these rules. The result is that the $n$th element of the argument interface list simply wraps the static terms $\sana{n}{\st}$ and $\ssyn{n}$.
